Spatial Analysis

### 2021-11-29 Scripts/spatial_analisis.Rmd
Changed F3 to positive/negative scale

grids_fp <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
) %>%
  mutate(spatial = "fp")

@@

unique(historic_spp$spp)
unique(historic_spp$region)
unique(historic_spp$season)

@@

reg_unit <- state_fit %>% 
  filter(season == "Spring") %>% 
  spread(spatial,mean_per) %>% 
  # Set NA's to 0 because no data found on FP
  mutate(fp = replace_na(fp,0)) %>%
  # View()
  mutate(
    difference = abs(fp-sw),
    difference = ifelse(difference > 100,100,
                        ifelse(difference < -100,-100,difference)
    )
  ) %>% 
  gather("spatial","mean_per",fp:difference) %>% 
  mutate(spp = gsub(" ","\n",spp),
         spatial = ifelse(spatial == "fp","Fishing ports",
                          ifelse(spatial == "sw","State waters","Difference")
         )
  )

@@

diff_plot <- land_sf %>% 
  left_join(reg_unit,
            by = "state") %>% 
  filter(spatial == "Difference") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
                              breaks = seq(0,25,5),
                              limits=(c(0,25)),
                              # labels = c("<-10",seq(-75,75,25),">100")
                              ) +
  facet_grid(spatial~ spp+label) +
  labs(x = "", 
       y = "") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line"),
        strip.background = element_blank(),
        strip.text.x = element_blank()
        )

@@

# Get seasonal data
season_fit <- state_fit %>% 
  filter(spatial != "fp") %>%
  spread(season,mean_per) %>%
  mutate(
    Difference = abs(Fall-Spring),
    Difference = ifelse(Difference > 100,100,
                        ifelse(Difference < -100,-100,Difference)
    )
  ) %>% 
  gather("season","mean_per",Fall:Difference) %>% 
  mutate(spp = gsub(" ","\n",spp))

>>>>

grids_fp <- my_path("D", "Partial/grid_fp", name = "grid_eez_fp_df.csv", read = T
) %>%
  mutate(spatial = "fp",
  spp = ifelse(spp == "summer flounder","Paralichthys dentatus", 
                 ifelse(spp == "scup", "Stenotomus chrysops", 
                        "Centropristis striata"
                 )
    )
  )

@@

# Data summary
c(unique(historic_spp$spp),
  unique(historic_spp$region),
  unique(historic_spp$season),
  unique(historic_spp$spatial)
)

@@

reg_unit <- state_fit %>% 
  filter(season == "Spring") %>% 
  spread(spatial,mean_per) %>% 
  # Set NA's to 0 because no data found on FP
  mutate(fp = replace_na(fp,0)) %>%
  # View()
  mutate(
    difference = fp-sw,
    difference = ifelse(difference > 100,100,
                        ifelse(difference < -100,-100,difference)
    )
  ) %>% 
  gather("spatial","mean_per",fp:difference) %>% 
  mutate(spp = gsub(" ","\n",spp),
         spatial = ifelse(spatial == "fp","Fishing ports",
                          ifelse(spatial == "sw","State waters","Difference")
         )
  )

@@

diff_plot <- land_sf %>% 
  left_join(reg_unit,
            by = "state") %>% 
  filter(spatial == "Difference") %>% 
  ggplot() +
  geom_sf(aes(fill = mean_per)) +
  # viridis::scale_fill_viridis("Difference (%)", alpha = 0.8,option = "C",
  #                             breaks = seq(0,25,5),
  #                             limits=(c(0,25)),
  #                             # labels = c("<-10",seq(-75,75,25),">100")
  #                             ) +
  scale_fill_gradient2("% Difference\n(fp-sw)", 
                       breaks = seq(-14,35,7),
                       limits=(c(-14,35)),
                              # labels = c("<-10",seq(-75,75,25),">100")
                              ) +
  facet_grid(spatial~ spp+label) +
  labs(x = "", 
       y = "") +
  my_ggtheme_p(facet_tx_s = 20,
               leg_pos = "bottom",
               axx_tx_ang = 45,
               ax_tx_s = 12,
               ax_tl_s = 18,
               hjust = 1) +
  theme(legend.key.width = unit(4,"line"),
        strip.background = element_blank(),
        strip.text.x = element_blank()
        )

@@

# Get seasonal data
season_fit <- state_fit %>% 
  filter(spatial != "fp") %>%
  spread(season,mean_per) %>%
  mutate(
    Difference = Fall-Spring,
    Difference = ifelse(Difference > 100,100,
                        ifelse(Difference < -100,-100,Difference)
    )
  ) %>% 
  gather("season","mean_per",Fall:Difference) %>% 
  mutate(spp = gsub(" ","\n",spp))
